---
title: "Mordvin Varieties"
date: "9/2/2019"
author: "Jack Rueter"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, echo=FALSE, warning=FALSE, message=FALSE}
source("R/functions.R")
```

## Paasonen's Mordvin materials

### Map of Paasonen's fieldwork (1891–1912) of the Erzya and Moksha

These are all locales, Erzya and Moksha, where fieldwork materials
were collected for and Heikki Paasonen 1891–1912. 
The dialects of each language within the Republic of Mordovia 
have been classified as five groups by Aleksandr Pavlovich Feoktistov. 
The some locales have not been classified, especially outside of the
Republic, and other locales have more than one classification.
By clicking the dot, you will reveal the location. (https://www.sgr.fi/fi/items/show/413)


```{r,echo=FALSE, warning=FALSE, message=FALSE}
make_mordva_map("PMW_locale_01.csv")
```

### Map of Paasonen's Erzya fieldwork (1891–1912)

These are Erzya locales where fieldwork materials
were collected for and by Heikki Paasonen 1891–1912.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_mordva_map("PMW_Erzya-locale_01.csv")
```


### Map of Paasonen's Moksha fieldwork (1891–1912)

These are Moksha locales where fieldwork materials
were collected for and by Heikki Paasonen 1891–1912.


```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_mordva_map("PMW_Moksha-locale_01.csv")
```

| code | name  |
|------|-------|
|mdf:C|Moksha, Central Dialect|
|mdf:Mixed| Moksha, Mixed Dialect|
|mdf:SE| Moksha, Southeast Dialect|
|mdf:Trans| Moksha, Transitional Dialect|
|mdf:W| Moksha, Western Dialect|
|mdf:X| Moksha, Undetermined Dialect|
|myv:C| Eryza, Central Dialect|
|myv:Mixed| Eryza, Mixed Dialect|
|myv:NW| Eryza, Northwest Dialect|
|myv:SE| Eryza, Southeast Dialect|
|myv:SW| Eryza, Southwest Dialect|
|myv:Trans| Eryza, Transitional Dialect|
|myv:W| Eryza, Western Dialect|
|myv:X| Eryza, Undetermined Dialect|


### Feoktistov & Saarinen, 2005 Moksha Dialects

These are Moksha locales identified as dialect collection points in:

* Feoktistov, Aleksandr & Saarinen, Sirkka. 2005. _Mokšamordvan murteet_. Suomalais-Ugrilaisen Seuran Toimituksia 249.  – Helsinki: Suomalais-Ugrilainen Seura. (https://www.sgr.fi/fi/items/show/111)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_Feok2005_map("Feoktistov-Saarinen_2005-Moksha-sources_collection-locales.tsv")
```

### Mordvin settlements in Bashkortostan (2014)

The data for this article is derived from the All-Russian census 2010.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_Bashk2014_map("Narody-Bashkortostana-enciklopedia-2014_Mordva-locales.tsv")
```

| code | name  |
|------|-------|
|Bask-group| Mixed Dialects, Bashkortostan|
|CD-Atj-group|Central Dialect, Atûrevo group|
|CD-E-group|Central Dialect, East group|
|CD-Jeln-group|Central Dialect, Jelʼnikov group|
|CD-Krasn-group|Central Dialect, Krasnoslobodsk group|
|CD-NE-group|Central Dialect, Northeast group|
|CD-Ruz-group|Central Dialect, Ruzaevka group|
|CD-Temn-group|Central Dialect, Temnikov group|
|MixD-N-group|Mixed Dialect, North group|
|MixD-S-group|Mixed Dialect, South group|
|MixD-SE-group|Mixed Dialect, Southeast group|
|SED|Southeast Dialect|
|TrD-SW-group|Transitional Dialect, Southwest group|
|TrD-wedge|Transitional Dialect, Wedge|
|WD-N-group|Western Dialect, North group|
|WD-S-group|Western Dialect, South group|
|NA|No dialect assigned|


### Mordvin populus attested in from census registry (2002)

The data is derived from the All-Russian census 2002 as provided in *Mokšamordvan murteet* (2005), this means that the settlements in Khazakhstan, Armenia and other places outside the Russian Federation are not shown.

* Feoktistov, Aleksandr & Saarinen, Sirkka. 2005. _Mokšamordvan murteet_. Suomalais-Ugrilaisen Seuran Toimituksia 249.  – Helsinki: Suomalais-Ugrilainen Seura. (https://www.sgr.fi/fi/items/show/111)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
make_census2002_map("2002-census-mordvin-pop.tsv")
```

| code | name  |
|------|-------|
|E| Erzya|
|M|Moksha|
|x|Undocumented|

