#Rscript build_database.R
---
output: 
  html_document:
    output_dir: docs
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- '..';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'database.html')) })
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning = FALSE)
library(tidyverse)
library(DT)
library(leaflet)
library(htmltools)

comparison <- read_csv("database.csv") %>%
  mutate(comment = case_when(is.na(comment) ~ "",
                             TRUE ~ as.character(comment)))

# This is not an elegant way to do this, but I have to think it
# some other day a bit longer
coordinates <- read_csv("coordinates.csv") %>%
  filter(language %in% comparison$language)

create_map <- function(data, feature_name){

        my_colors <-
          c(
            "#1f77b4",
            "#ff7f0e",
            "#2ca02c",
            "#d62728",
            "#9467bd",
            "#8c564b",
            "#e377c2",
            "#7f7f7f",
            "#17becf",
            sample(grDevices::colors()[!grepl("ivory|azure|white|gray|grey|black|pink|1",
                                              grDevices::colors())])
          )
          corpus <- data
          current_selection <- corpus %>% 
            filter(feature == feature_name) %>%
            arrange(language)
          pal <- colorFactor({my_colors[1:length(unique(current_selection$value))]},
                                      domain = current_selection$value)

          title_text <- current_selection$feature[1] %>% as.character()

          leaflet(data = current_selection) %>%
            addTiles() %>%
            addCircleMarkers(lng = ~longitude,
                             lat = ~latitude,
                             color = ~pal(value),
                             radius = 8,
                             stroke = FALSE, fillOpacity = 0.8,
                             popup = ~language) %>%
            addLegend("bottomleft", pal = pal, values = ~value,
                      title = title_text,
                      opacity = 1
            )

}

```

###  Comparative database of Mordvin varieties {.tabset .tabset-fade .tabset-pills}

#### About

The data is shared under CC-0.

#### Search {.tabset .tabset-fade .tabset-pills}

```{r}

datatable(comparison, filter = 'top', rownames = FALSE, options = list(dom = 'tip'), escape = FALSE)

```

#### Maps {.tabset .tabset-fade .tabset-pills}

This section contains automatically generated maps of all presented features.

```{r}

comparison <- comparison %>%
  filter(language %in% coordinates$language)

map_chunks <- comparison %>%
  distinct(feature) %>%
  pull(feature) %>%
  map(~ {create_map(comparison %>% left_join(coordinates, by = "language"), .x)})


tagList(map_chunks)

```
